Utilizing Design Principles from Glass Sponges for Structurally Robust Lattices

### 2018-08-23 Paper-FernandesWeaverBertoldi_AdvMaterials_2018.tex
Updates from ShareLaTeX

\begin{document}
\maketitle
% \doublespace
%\linenumbers

\section{Introduction}
\subsection{Sponge Biology}
\subsection{History of Diagonally Reinforced Structures and Previous Works}
\subsection{Examples of Current Diagonally Reinforced Designs}

\section{Methods}
\subsection{Numerical Model Setup}
\subsection{Experimental Design}

\section{Results}
\subsection{Linear Stiffness for different Designs}
 \subsection{Buckling Resistance for Different Designs}
\subsection{Experimental Results}

\section{Discussion}
\subsection{Parameter Exploration}
\subsection{Parameter Optimization}

\section{Conclusion}

\section*{Acknowledgments}
\section*{References}

@@

% \section{Introduction}
The foundational structure of diagonal reinforcement for truss systems found in bridges, buildings, and beam structures has not changed much since the introduction of the Long truss design patented by Colonel Long in 1830 \citep{waddell1916}. In modern day structures, we see many different iterations of new truss designs with various applications in mind but with what is the same fundamentally simple diagonal reinforcement technique. This technique, involving two diagonal trusses (one in each direction) crossing the opening of a square beam cell, limits the transverse motion of the main support beams ultimately giving the structure shear capacity and strength. Alternative, methods to strengthen beam structures have been introduced via material \hl{[...],} \mf{needs more information and citations}. However, in this study we seek to further strengthen square lattices through inspiration from a particular sponge species called \textit{Euplectella Aspergillum}, commonly known as the Venus' flower basket. This particular species, which is part of the \textit{Hexactinellid} class, is primarily made of silica and exhibit a periodic and regular grid structure with an intrinsic and different diagonal reinforcement scheme.

@@

In order to study the impact of diagonal separation for Design A (sponge design), we perform a parametric study on the buckling behavior of the structure under varying separation distances ($C$). Note, we do not perform a stiffness test as the linear stiffness is not dependent on design but instead depends on the mass ratio between diagonal and non-diagonal elements as well as the diagonal element's angles. \Cref{Fig5}(a) shows the buckling behavior as a function of the non-dimensional separation ($C/L$). Where at $C/L=0$ we obtain Design B, and at $C/L=0.5$ we obtain diamond shaped reinforcement alignment.

@@

\Cref{Fig5}(b) shows the structural stiffness as a function of $\lambda$ for various loading angles (corresponding to the respective colors). In this figure, we see that for small $\lambda$ the structure is stiffer at $0^\circ$ loading and for large $\lambda$ the structure is stiffer at $45^\circ$. This is expected as we are allocating more material to its respective elements. Furthermore, we can see that at $\lambda=1$ we attain a point in the mass ratio where the stiffness is equal for all angles. That is because there is the same amount of material allocated to the diagonals as there is to the non-diagonal elements.

\Cref{Fig5}(c) illustrates the critical buckling strain as a function of $\lambda$. Here, we can clearly see that buckling strain is dependent on the mass ratio and behaves differently for all angles \hl{[...]} \mf{I am not sure what to say here (interpretation) about this graph.}

>>>>

\begin{document}
\maketitle
% \doublespace
\linenumbers

% \section{Introduction}
% \subsection{Sponge Biology}
% \subsection{History of Diagonally Reinforced Structures and Previous Works}
% \subsection{Examples of Current Diagonally Reinforced Designs}

% \section{Methods}
% \subsection{Numerical Model Setup}
% \subsection{Experimental Design}

% \section{Results}
% \subsection{Linear Stiffness for different Designs}
%  \subsection{Buckling Resistance for Different Designs}
% \subsection{Experimental Results}

% \section{Discussion}
% \subsection{Parameter Exploration}
% \subsection{Parameter Optimization}

% \section{Conclusion}

% \section*{Acknowledgments}
% \section*{References}

@@

% \section{Introduction}

In modern day structural engineering, we find many

The design of diagonal reinforcement for truss systems found in bridges, buildings, and beam structures has not changed much since the introduction of the Long truss design patented by Colonel Long in 1830 \citep{waddell1916}. In modern day structures, we see many different iterations of new truss designs with various applications in mind but with what is the same fundamentally simple diagonal reinforcement technique. This technique, involving two diagonal trusses (one in each direction) crossing the opening of a square beam cell, limits the transverse motion of the main support beams ultimately giving the structure shear capacity and strength. Alternative, methods to strengthen beam structures have been introduced via material \hl{[...],} \mf{needs more information and citations}. However, in this study we seek to further strengthen square lattices through inspiration from a particular sponge species called \textit{Euplectella Aspergillum}, commonly known as the Venus' flower basket. This particular species, which is part of the \textit{Hexactinellid} class, is primarily made of silica and exhibit a periodic and regular grid structure with an intrinsic and different diagonal reinforcement scheme.

@@

In order to study the impact of diagonal separation for Design A (sponge design), we perform a parametric study on the buckling behavior of the structure under varying separation distances ($C$). Note, we do not perform a stiffness test as the linear stiffness is not dependent on design but instead depends on the mass ratio between diagonal and non-diagonal elements as well as the diagonal element's angles. {Fig5}(a) shows the buckling behavior as a function of the non-dimensional separation ($C/L$). Where at $C/L=0$ we obtain Design B, and at $C/L=0.5$ we obtain diamond shaped reinforcement alignment.

@@

{Fig5}(b) shows the structural stiffness as a function of $\lambda$ for various loading angles (corresponding to the respective colors). In this figure, we see that for small $\lambda$ the structure is stiffer at $0^\circ$ loading and for large $\lambda$ the structure is stiffer at $45^\circ$. This is expected as we are allocating more material to its respective elements. Furthermore, we can see that at $\lambda=1$ we attain a point in the mass ratio where the stiffness is equal for all angles. That is because there is the same amount of material allocated to the diagonals as there is to the non-diagonal elements.

{Fig5}(c) illustrates the critical buckling strain as a function of $\lambda$. Here, we can clearly see that buckling strain is dependent on the mass ratio and behaves differently for all angles \hl{[...]} \mf{I am not sure what to say here (interpretation) about this graph.}
